Re-finding to support a Deep Web Question Answering System

### 2010-03-04 paper/semsearch10/content/ontological_realms.tex
After Dr. Wilson's improvements

\subsection{Class Heterarchy} 
% Author: Clint 
Since, our representation of semi structured query [citation needed] is in OWL ontology format, and our aim is to compare and rank the queries in this format, we had to define a similarity measure between ontologies. The defined ontology class comparison measure "class divergence" [citation needed] assumes that we have an ontology store with unambiguous interpretation of classes and strict hierarchical subclass super class relationships and the classes to be compared should belong to it. We cannot find any robust existing ontology library of that nature for this purpose. So we decided to build a new ontology store and as an initial step the categories from DBPedia store [citation needed] are used. Even though, some of these categories are loosely coupled and not fully agreed upon the sub category and super category relationships, this DBPedia has enormous amount of data in linked form [citation needed]. The OWL ontology [citation needed] format is followed in this process. The DBPedia categories are converted into OWL ontology classes and the super class - sub class relationships are built using the OWL super class sub class axioms [citation needed]. Another reason for selecting OWL for this purpose is that we can make use of the existing APIs for building and reasoning [citation needed] the ontology relationships.

%-------------------------------------------------------------------------------

Building Ontological Realms

Once the semantic hierarchy is created, the next step is to create training data for the system. The task is then to grab the pages, build a corpus relating to a given category, and then compile the information in a meaningful way. The overall goal is to grab enough information to properly characterize a category while limiting the amount of unnecessary content within the corpus. The problem with this approach is the page density varies greatly across the heterarchy. Each category within the DBpedia/Wikipedia heterarchy contains a set of information pages, P, that correspond to concepts that share said category. Considering that the categorical structure is a directed acyclic graph  \cite{Suchanek07yago:a}, we consider the use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing a particular category. The assumption is that a node can be fully described by its ancestor, descendant, and spousal nodes (parent node of subcategory not equal to the category). While this does not completely solve the issue of a category residing in a sparse area of the graph, the amount of information that can be obtained per blanket is usually more helpful than per category.

Consider the abbreviated Markov blanket for the category Automobiles:

% figure: abbreviated Markov blanket for the category Basketball  
\begin{figure}[t]
\centering
\includegraphics[width=90mm]{abbrv_bb_blanket.eps}
\caption{Abbreviated Markov blanket for the category Basketball}
\label{fig:abbrv_bb_blanket}
\end{figure}

@@

\begin{lstlisting}[language=Python,frame=single,tabsize=2,caption=BlanketSubjectRetreival, label=BlanketSubjectRetreival]
def BlanketSubjectRetreival(blanket, maxLevel):
	for category in blanket:
		subjectSet.add(grabsubjects(category))
		diff = afterSize - beforeSize
		if diff <= \alpha and category is subcategory:
			PlusOneMechanism(category, maxLevel)
	return subjectSet
\end{lstlisting}

\begin{lstlisting}[language=Python,frame=single,tabsize=2,caption=PlusOneMechanism, label=PlusOneMechanism]
def PlusOneMechanism(category, level):
	plusOneSet = grabPlusOneSubcategories(category)
	for subcategory in plusOneSet:
		subject.add(grabSubjects

>>>>

\section{Representing and Ontological Realms}
Two types of ontologies are used by our system:
\begin{enumerate}
\item Realm ontologies, comprising a heterarchy of categories that
  characterize terms that can appear in queries.
\item SSQ ontologies, used to describe the form of particular
  realm-specific queries.
\end{enumerate}
For any particular ontological realm, the number of potential
terms and their associated categories can be quite large.
Construction of a realm ontology and the terms associated
with its categories would be an extremely laborious task
for any non-trivial realm. The realm of automobiles (which
we use for illustration in this paper) contains, for example,
over XXXX categories and XXXX terms. We were unable to find
an appropriate ontology for this realm, so we constructed it
using categories from the DBPedia [!!!! citation needed].
The primary benefit of using the DBPedia for this purpose is
that not only does it supply a categorical heterarchy, but it
also links to wikipedia documents which provides us with a large
realm-specific document corpus.
\subsection{Category Heterarchy}

To support our process, we map DBPedia categories into classes in our
realm ontology with the superclass/subclass relationships built using
DBPedia properties broader/narrower.  By using OWL, we can exploit the
OWL API for matching SSQ ontologies that reference these realm
ontologies.

%Start with a collection of relevant categories

Once the semantic hierarchy is created, the next step is to create
training data for the system. The task is then to grab the pages,
build a corpus relating to a given category, and then compile the
information in a meaningful way. The overall goal is to grab enough
information to properly characterize a category while limiting the
amount of unnecessary content within the corpus. The problem with this
approach is the page density varies greatly across the
heterarchy. Each category within the DBpedia/ Wikipedia heterarchy
contains a set of information pages, P, that correspond to concepts
that share said category. Considering that the categorical structure
is a directed acyclic graph \cite{Suchanek07yago:a}, we consider the
use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing
a particular category. The category's that The assumption is that a
node can be fully described by its ancestor, descendant, and spousal
nodes (parent node of subcategory not equal to the category). While
this does not completely solve the issue of a category residing in a
sparse area of the graph, the amount of information that can be
obtained per blanket is usually more helpful than per category.

@@

\begin{lstlisting}[language=Python,frame=none,tabsize=2,caption=BlanketSubjectRetreival,label=BlanketSubjectRetreival,basicstyle=\small]
def BlanketSubjectRetreival(blanket, maxLevel):
	for category in blanket:
		subjectSet.add(grabsubjects(category))
		diff = afterSize - beforeSize
		if diff <= a and category is subcategory:
			PlusOneMechanism(category, maxLevel)
	return subjectSet
\end{lstlisting}

\begin{lstlisting}[language=Python,frame=none,tabsize=2,caption=PlusOneMechanism, label=PlusOneMechanism,basicstyle=\small]
def PlusOneMechanism(category, level):
	plusOneSet = grabPlusOneSubcategories(category)
	for subcategory in plusOneSet:
		subject.add(grabSubjects(subcategory))
		diff = afterSize - beforeSize
		if diff <= a and level > 0:
			PlusOneMechanism(subcategory, level-1)

### 2010-03-04 paper/semsearch10/content/ssq_ranking.tex
After Dr. Wilson's improvements

\subsection{SSQ Ranking}
\label{sec:ssq}
In order to match a new query with a SSQ within our data store, we
have defined similarity measures between the ontologies of the new
query and the candidate SSQs. These measures capture the distance
between the ontology classes, properties, and individuals at the
conceptual level in addition to simply matching URIs. The similarity
measures are implemented in two scenarios: \textit{on-line execution}
and \textit{off-line mode}. The \textit{on-line execution} is time
sensitive and is used primarily for relating newly defined SSQs to the
SSQs in the store. During \textit{off-line execution}, the system
clusters similar SSQs.

The similarity measure for the SSQ ontologies is determined by the
following components.
\begin{enumerate}
    \item QueryClass: an OWL class and the root of the SSQ ontology
      structure.
    \item hasRealm: an OWL object property with its domain as the SSQ
      Query class and its range as a realm class.
    \item Contexts such as who, what, when, and where are OWL object
      properties, whose domains are the query classes and ranges are
      OWL classes.
    \item SSQClass: an OWL class which is created from the components
      described above.
\end{enumerate}
Based on this ontology structure and the execution scenarios, we have
created an algorithm for finding the matches between SSQ
ontologies. It is based on class divergence, which is motivated by the
concept of multiple dispatch in CLOS \cite{95411} and Dylan
programming \cite{DBLP:conf/oopsla/BarrettCHMPW96} for generic
function type matches. We consider the realm class and context
property ranges for determining SSQ similarity. Subsections
\ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.

@@

% Need to show an example ?

>>>>

\section{SSQ Ranking}
\label{sec:ssq}
In order to match a new query with a SSQ within our data store, we
have defined similarity measures between the ontologies of the new
query and the candidate SSQs. These measures capture the distance
between the ontology classes, properties, and individuals at the
conceptual level in addition to simply matching URIs. The similarity
measures are implemented in two scenarios: \textit{on-line execution}
and \textit{off-line mode}. The \textit{on-line execution} is time
sensitive and is used primarily for relating newly defined SSQs to the
SSQs in the store. During \textit{off-line execution}, the system
clusters similar SSQs.

The similarity measure for the SSQ ontologies is determined by the
following components.
\begin{enumerate}
    \item QueryClass: an OWL class and the root of the SSQ ontology
      structure.
    \item hasRealm: an OWL object property with its domain as the SSQ
      Query class and its range as a realm class.
    \item Contexts such as who, what, when, and where are OWL object
      properties, whose domains are the query classes and ranges are
      OWL classes.
    \item SSQClass: an OWL class which is created from the components
      described above.
\end{enumerate}
Based on this ontology structure and the execution scenarios, we have
created an algorithm for finding the matches between SSQ
ontologies. It is based on class divergence, which is motivated by the
concept of multiple dispatch in CLOS \cite{95411} and Dylan
programming \cite{DBLP:conf/oopsla/BarrettCHMPW96} for generic
function type matches. We consider the realm class and context
property ranges for determining SSQ similarity. Once we have the similarity measures between the user defined SSQ and relevant QRMs in the store, we can order the relevant QRMs. The order provides a ranking for the results to the user. Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.

@@
